Supplementary material: The increasing cost of happiness

### 2021-10-27 src/supplementary-html.Rmd
Final response to Reviewer 1. Closes issue #27

bind_rows(
  map_dfr(nested_models$log_fit, broom::glance) %>%
    mutate(model = "log", year = 2001:2019),
  map_dfr(nested_models$lin_fit, broom::glance) %>%
    mutate(model = "lin", year = 2001:2019),
  map_dfr(nested_models$pw_fit, broom::glance) %>%
    mutate(model = "pw", year = 2001:2019),
  map_dfr(nested_models$log_fit_c, broom::glance) %>%
    mutate(model = "logc", year = 2001:2019),
  map_dfr(nested_models$lin_fit_c, broom::glance) %>%
    mutate(model = "linc", year = 2001:2019),
  map_dfr(nested_models$pw_fit_c, broom::glance) %>%
    mutate(model = "pwc", year = 2001:2019)
) -> model_summaries
```
```{r model_summaries_allyears}
df <- unnest(nested_data, cols = c(data)) %>% ungroup()

@@

model_summaries_all <- rbind(
  broom::glance(lm_fit) %>% mutate(model = "lin", year = "Overall"),
  broom::glance(lm_fit_c) %>% mutate(model = "linc", year = "Overall"),
  broom::glance(log_fit) %>% mutate(model = "log", year = "Overall"),
  broom::glance(log_fit_c) %>% mutate(model = "logc", year = "Overall"),
  broom::glance(pw_fit) %>% mutate(model = "pw", year = "Overall"),
  broom::glance(pw_fit_c) %>% mutate(model = "pwc", year = "Overall"),
  model_summaries
)
```

##### Table S4. In-sample fit statistics (adj. R-squared) for affective wellbeing and income 
```{r table_s4}
model_summaries_all %>%
  select(model, Year = year, adj.r.squared) %>%
  spread(model, adj.r.squared) %>%
  flextable() %>%
  colformat_double(j = 2:7, digits = 3) %>%
  set_header_labels(
    lin = "Linear", 
    linc = "Linear\n(conditional)",
    log = "Log-linear",
    logc = "Log-linear\n(conditional)",
    pw = "Piecewise",
    pwc = "Piecewise\n(conditional)") %>%
  valign(i = 1, valign = "top", part = "header") %>%
  fontsize(size = 9.5, part = "all") %>%
  width(j = 2:7, width = 1) %>%
  width(j = 1, width = .5)
```

@@

##### Table S5. OLS coefficients from linear, log-linear and piecewise models  
```{r table_s5}
lm_coef <- map_dfr(nested_models$lin_fit, broom::tidy, .id = "Year") %>%
  filter(term == "dollars") %>%
  mutate(coefficient = paste0(round(estimate, 3), " (", round(std.error, 3), ")")) %>%
  select(Year, `linear (se)` = coefficient)

log_coef <- map_dfr(nested_models$log_fit, broom::tidy, .id = "Year") %>%
  filter(term == "log(dollars)") %>%
  mutate(coefficient = paste0(round(estimate, 3), " (", round(std.error, 3), ")")) %>%
  select(Year, `log-linear (se)` = coefficient)

pw_coefs <- map_dfr(nested_models$pw_fit, broom::tidy, .id = "Year") %>%
  filter(term %in% c("dollars", "U1.dollars")) %>%
  select(Year, term, estimate, std.error) %>%
  pivot_wider(id_cols = Year, 
              names_from = term, 
              values_from = estimate:std.error) %>%
  mutate(
    estimate_post = estimate_U1.dollars + estimate_dollars,
    `pre-slope (se)` = paste0(
      round(estimate_dollars, 3), " ±", round(std.error_dollars, 3)),
    `post-slope (se)` = paste0(
      round(estimate_post, 3), " ±", round(std.error_U1.dollars, 3))
    ) %>%
  select(Year, `pre-slope (se)`, `post-slope (se)`)

pw_coefs <- map_dfr(nested_models$pw_fit, ~as_tibble(.x$psi), .id = "Year") %>%
  mutate(term = "psi.dollars") %>%
  mutate(coefficient = paste0(round(`Est.`, 2)*10, " (", round(`St.Err`, 2)*10, ")")) %>%
  select(Year, `change point ($000s ±se)` = coefficient) %>%
  left_join(pw_coefs)

left_join(lm_coef, log_coef, by = "Year") %>%
  left_join(pw_coefs, by = "Year") %>%
  mutate(Year = as.character(2000 + as.numeric(Year))) %>%
  flextable() %>%
  fontsize(size = 9.5, part = "all") %>%
  autofit()
```

>>>>

bind_rows(
  map_dfr(nested_models$log_fit, broom::glance) %>%
    mutate(model = "log", year = 2001:2019),
  map_dfr(nested_models$lin_fit, broom::glance) %>%
    mutate(model = "lin", year = 2001:2019),
  map_dfr(nested_models$pw_fit, broom::glance) %>%
    mutate(model = "pw", year = 2001:2019),
  map_dfr(nested_models$log_fit_c, broom::glance) %>%
    mutate(model = "logc", year = 2001:2019),
  map_dfr(nested_models$lin_fit_c, broom::glance) %>%
    mutate(model = "linc", year = 2001:2019),
  map_dfr(nested_models$pw_fit_c, broom::glance) %>%
    mutate(model = "pwc", year = 2001:2019)
) -> model_summaries
```

##### Table S4. MLE coefficients from piecewise-linear, linear, log-linear OLS models   
```{r table_s4}
lm_coef <- map_dfr(nested_models$lin_fit, broom::tidy, .id = "Year") %>%
  mutate(
    coefficient = paste0(round(estimate, 2), "\n(", round(std.error, 2), ")")
    ) %>%
  select(Year, term, coefficient) %>%
  spread(term, coefficient) %>%
  rename("b0_lin" = 2, "b1_lin" = 3)

log_coef <- map_dfr(nested_models$log_fit, broom::tidy, .id = "Year") %>%
  mutate(
    estimate = ifelse(str_detect(term, "log"), estimate/10, estimate),
    std.error = ifelse(str_detect(term, "log"), std.error/10, std.error),
    coefficient = paste0(round(estimate, 2), "\n(", round(std.error, 2), ")")
    ) %>%
  select(Year, term, coefficient) %>%
  spread(term, coefficient) %>%
  rename("b0_log" = 2, "b1_log" = 3)

pw_coefs <- map_dfr(nested_models$pw_fit, broom::tidy, .id = "Year") %>%
  filter(term %in% c("(Intercept)", "dollars", "U1.dollars")) %>%
  select(Year, term, estimate, std.error) %>%
  pivot_wider(id_cols = Year, 
              names_from = term, 
              values_from = estimate:std.error) %>%
  mutate(
    b0_pw = paste0(
      round(`estimate_(Intercept)`, 2), "\n(", round(`std.error_(Intercept)`, 2), ")"),
    estimate_post = estimate_U1.dollars + estimate_dollars,
    b1_pw = paste0(
      round(estimate_dollars, 2), "\n(", round(std.error_dollars, 2), ")"),
    b2_pw = paste0(
      round(estimate_post, 2), "\n(", round(std.error_U1.dollars, 2), ")")
    ) %>%
  select(Year, b0_pw, b1_pw, b2_pw)

pw_coefs <- map_dfr(nested_models$pw_fit, ~as_tibble(.x$psi), .id = "Year") %>%
  mutate(term = "psi.dollars") %>%
  mutate(Omega = paste0(round(`Est.`, 3)*10, "\n(", round(`St.Err`, 3)*10, ")")) %>%
  select(Year, Omega) %>%
  left_join(pw_coefs)

left_join(lm_coef, log_coef, by = "Year") %>%
  left_join(pw_coefs, by = "Year") %>%
  mutate(Year = as.character(2000 + as.numeric(Year))) %>%
  arrange(Year) %>%
  flextable(
    col_keys = c("Year", "b0_pw", "b1_pw", "b2_pw", "Omega", "break1", "b0_log", 
                 "b1_log", "break2", "b0_lin", "b1_lin") # 11 columns
  ) %>%
  merge_v(j = 1) %>%
  set_header_labels(values = c(b0_pw = paste0("\u03b2", "0"),
                               b1_pw = paste0("\u03b2", "1"),
                               b2_pw = paste0("\u03b2", "2"),
                               Omega = "\u03C9",
                               b0_log = paste0("\u03b2", "0"),
                               b1_log = paste0("\u03b2", "1"),
                               b0_lin = paste0("\u03b2", "0"),
                               b1_lin = paste0("\u03b2", "1"))) %>%
  add_header(top = TRUE,
             values = c(b0_pw = "Piecewise-linear (±se)",
                        b1_pw = "Piecewise-linear (±se)",
                        b2_pw = "Piecewise-linear (±se)",
                        Omega = "Piecewise-linear (±se)",
                        b0_log = "Log-linear (±se)",
                        b1_log = "Log-linear (±se)",
                        b0_lin = "Linear (±se)",
                        b1_lin = "Linear (±se)")) %>%
  merge_h(part = "header") %>%
  width(j = 1, width = 0.5) %>%
  width(j = 2:11, width = 0.625) %>%
  width(j = c(6, 9), width = 0.1) %>%
  fontsize(size = 9, part = "all") %>%
  # flextable::theme_vanilla() %>% # theme_vanilla()
  valign(valign = "top") %>%
  valign(valign = "bottom", part = "header") %>%
  border_remove() %>%
  hline_top(part="header", border = officer::fp_border()) %>%
  hline_bottom(part="header", border = officer::fp_border()) %>%
  hline_bottom(part="body", border = officer::fp_border())
```

**In-sample fit statistics**. Our primary objective was to understand the relationships between the parameters of our model, and so in-sample fit statistics such as R^2^ are irrelevant for this objective. Moreover, our use of regularized priors will bias such in-sample estimates towards zero as regularization deliberately sacrifices in-sample variance for out-of-sample accuracy, which obviously hinders interpretation of the in-sample values. Nevertheless, some readers may find it useful to compare the in-sample fit statistics between the three different model types employed here: piecewise, linear and log-linear, as well as between the conditional and unconditional models. Because the usual fit statistics such as R^2^ present a problem for Bayesian fits, as the variance of the predicted values can be larger than the variance of the data results in R^2^ values greater than 1, we present the in-sample statistics from OLS model fits (without regularization or penalized likelihoods).

##### Table S5. Adjusted R-squared for affective wellbeing and income
```{r model_summaries_allyears}
df <- unnest(nested_data, cols = c(data)) %>% ungroup()

@@

model_summaries_all <- rbind(
  broom::glance(lm_fit) %>% mutate(model = "lin", year = "Overall"),
  broom::glance(lm_fit_c) %>% mutate(model = "linc", year = "Overall"),
  broom::glance(log_fit) %>% mutate(model = "log", year = "Overall"),
  broom::glance(log_fit_c) %>% mutate(model = "logc", year = "Overall"),
  broom::glance(pw_fit) %>% mutate(model = "pw", year = "Overall"),
  broom::glance(pw_fit_c) %>% mutate(model = "pwc", year = "Overall"),
  model_summaries
)
```
```{r table_s5}
model_summaries_all %>%
  select(model, Year = year, adj.r.squared) %>%
  spread(model, adj.r.squared) %>%
  flextable() %>%
  colformat_double(j = 2:7, digits = 3) %>%
  set_header_labels(
    lin = "Linear", 
    linc = "Linear\n(conditional)",
    log = "Log-linear",
    logc = "Log-linear\n(conditional)",
    pw = "Piecewise",
    pwc = "Piecewise\n(conditional)") %>%
  valign(i = 1, valign = "top", part = "header") %>%
  fontsize(size = 9.5, part = "all") %>%
  width(j = 2:7, width = 1) %>%
  width(j = 1, width = .5)
```

@@
